### 2023-09-26 SujetStage/2022-pNetsubjectM2.tex
biblio

\bibitem{henrio:Forte2016}
Henrio, L., Madelaine, E., Zhang, M.:
\newblock {A Theory for the Composition of Concurrent Processes}.
\newblock In Albert, E., Lanese, I., eds.: {36th International Conference on
  Formal Techniques for Distributed Objects, Components, and Systems (FORTE)}.
  Volume LNCS-9688 of Formal Techniques for Distributed Objects, Components,
  and Systems., Heraklion, Greece (June 2016)  175--194. 
\newblock  \url{https://hal.inria.fr/hal-01299562}

@@

\bibitem{hou:hal-02406098}
Hou, Z., Madelaine, E.:
\newblock {Symbolic Bisimulation for Open and Parameterized Systems}.
\newblock In: {PEPM 2020 - ACM SIGPLAN Workshop on Partial Evaluation and
  Program Manipulation}, New-Orleans, United States (January 2020). 
 \newblock \url{https://hal.inria.fr/hal-02406098}

\bibitem{arxiv-weakbisim}
Rabéa Ameur-Boulifa and Ludovic Henrio and Eric Madelaine:
\newblock {Compositional equivalences based on Open pNets}.
\newblock arXiv {2007.10770} (2021).
 \newblock \url{https://arxiv.org/abs/2007.10770}
\end{thebibliography}

>>>>

\bibitem{henrio:Forte2016}
Ludovic Henrio, Eric Madelaine, Min Zhang:
\newblock {A Theory for the Composition of Concurrent Processes}.
\newblock In Albert, E., Lanese, I., eds.: {36th International Conference on
  Formal Techniques for Distributed Objects, Components, and Systems (FORTE)}.
  Volume LNCS-9688 of Formal Techniques for Distributed Objects, Components,
  and Systems., Heraklion, Greece (June 2016)  175--194. 
\newblock  \url{https://hal.inria.fr/hal-01299562}

@@

\bibitem{hou:hal-02406098}
Zechen Hou,  Eric  Madelaine:
\newblock {Symbolic Bisimulation for Open and Parameterized Systems}.
\newblock In: {PEPM 2020 - ACM SIGPLAN Workshop on Partial Evaluation and
  Program Manipulation}, New-Orleans, United States (January 2020). 
 \newblock \url{https://hal.inria.fr/hal-02406098}

\bibitem{arxiv-weakbisim}
Rabéa Ameur-Boulifa, Ludovic Henrio, Eric Madelaine:
\newblock {Compositional equivalences based on Open pNets}.
\newblock Journal of Logical and Algebraic Methods in Programming, 2022, 131, p.100842..
 \newblock \url{https://hal.science/hal-03894031}
\end{thebibliography}
